\setchapterpreamble[u]{\margintoc}
\chapter{Conclusions}
\begin{fullwidth}
This thesis aims to be an overview of the {\sffamily MV} model along with the gluon saturation which emerges within its framework, and of some basic notions from relativistic viscous hydrodynamics. These approaches are numerically implemented in simulation codes publicly available. The initial conditions arising from {\sffamily CGC} initial conditions are coupled to viscous hydrodynamics and the final results are compared to experimental data from {\sffamily RHIC} for {\sffamily Au+Au} collisions at $\sqrt{s_\textsf{NN}}=200$ GeV, providing satisfactory results when both shear and bulk viscosities are taken into account. This is of course a minimal hybrid approach and more stages must be included for a better description of heavy-ion collisions. 
\end{fullwidth}

\vspace{2cm}

\begin{fullwidth}
\begin{quote}
  {\itshape ``He had once tasted the experience that the Game could be played in a supreme and sacred sense; but he had also seen that the majority of players and students of the Game, and even some of the leaders and teachers, by no means shared that lofty and sacramental feeling for the Game. They did not regard the Game language as a lingua sacra, but more as an ingenious kind of stenography. They practiced the Game as an interesting or amusing specialty, an intellectual sport or an arena for ambition.[...] In short, he had doubts and divided feelings; the Game was a vital question for him, had become the chief problem of his life, and he was by no means disposed to let well-meaning spiritual guides ease his struggles or benignly smiling teachers dismiss them as trivial.``}
  \begin{flushright}
    Hermann Hesse, {\sffamily\color{ming} The Glass Bead Game}
  \end{flushright}
\end{quote}
\end{fullwidth}

\chapter*{Acknowledgments}
\begin{fullwidth}
\begin{quote}
I thank my supervisor Prof. Dr. Mihai Petrovici for offering me the opportunity to emerse myself in this beautiful topic. I am extremely grateful to D. M{\"u}ller for the helpful disscusions and his tremendous help with {\sffamily Curraun} and the Landau matching. S. Micluta's technical advice and knowledge of numerical methods was invaluable. Most importantly, I want to express my deepest gratitude to my parents and to my dear Vlad. 
\end{quote}
\end{fullwidth}


\labch{conc}